Draft Research pt1

### 2019-03-08 draftResearch_pt1.Rmd
Concatenated eligible positions to single comma delimited character vector

# Position Eligibility
```{r}
(get_players(50) -> tst_results)

tst_results %>%
  select(starts_with("eligible_positions")) %>%
  transpose() %>%
  lapply(as.character) %>%
  lapply(function(x) x[!is.na(x)]) -> pos_complete

# add list rows representing new column as new column on prior df?
tst_results %>%
  add_column(pos_complete) %>%
  select(1, pos_complete)

@@

>>>>

# Position Eligibility
```{r}
suppressWarnings(
  get_players(312) -> tst_results
)

col_nms <- tst_results %>%
  select(starts_with("eligible_positions")) %>%
  colnames()

tst_results %>%
  mutate(positions = paste(!!! syms(col_nms), sep = "," )) %>%
  mutate(positions = gsub('NA', '', positions)) %>%
  mutate(positions = gsub(',,', '', positions)) %>%
  select(-(starts_with("eligible_positions"))) %>%
  select(name.full, display_position, positions) -> tst_results

tst_results %>% saveRDS("data/tst_results")

View(tst_results)

@@

##### To Do

1. Prevent the need to supressWarnings 
2. Some merge of display position and positions
3. Rename df to something useful for joining to other data sets
4. Figure out what columns to include that will be needed for joining to other data sets
5. Kill trailing comma in positions column
